MYC overrides HIF-1α to regulate proliferating primary cell metabolism in hypoxia

### 2023-04-26 manuscript/manuscript.qmd
edit manuscript and figures

We observed a similar pattern using RNA interference to silence PHD2 expression (**Figure 8 - figure supplement 1**).

>>>>

We observed a similar effect of hypoxia on glycolysis when using RNA interference to silence PHD2 expression and activate HIF-1α gene transcription (**Figure 8 - figure supplement 1**).

These data indicate that the metabolic effects that we observe are not a consequence of off-target effects of BAY treatment.
